---
title: "XC Figures"
author: "Jesse Goodrich"
date: "12/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width=8, fig.height = 6.5, cache = FALSE)
library(tidyverse)
library(table1)
library(emmeans)
library(brglm)
library(ggpmisc)
library(car)
library(gridExtra)
library(lmerTest)
library(grid)
library(gtools)
library(MuMIn)
library(cowplot)
library(broom)
library(broom.mixed)
library(janitor)
library(nlme)

# Set ggplot theme
theme_set(theme_cowplot())
source(here::here("!directories.r"))
source(here::here("!load_xc_data.r"))
```


Table 2
```{r Table 2}
table(id$iron_def_acute , id$sex)
with(id %>% filter(sex == "Female", ery < 100), hist(stfr))

id <- id %>% 
  mutate(male_female_iron_def = if_else((iron_def_acute == "ID") & (sex == "Male"), "ID", as.character(acute_chronic_id)))

table1::table1(~ hgb + hct + ferritin + hepcidin + 
                 stfr + ery_cor + bili + percent_retic + IL1a + IL1b + IL2 + 
                 IL4 + IL6 +IL8 + IL10+ IL12p70 + IFNg + TNFa  | sex + male_female_iron_def,
               data = id,
               overall = FALSE)
ggplot(id, aes(cpk)) + 
  geom_density() + 
  facet_wrap(~sex, nrow = 2)

# Normal Vars
summaryBy(formula = hgb + hct + percent_retic + ferritin +  
            stfr + bili + cpk + ldh~ sex * male_female_iron_def,
          data = id %>%
            as.data.frame(),
          FUN = function(x){avg_sd_fxn(x, include.n = FALSE, n.digits = 0)}, 
          keep.names = TRUE) %>%
  as_tibble() %>% t() %>% noquote()

# Non normal vars
summaryBy(formula = hepcidin + ery_cor + IL1a + IL1b + IL2 +  
            IL4 + IL6 +IL8 + IL10 + IL12p70 + IFNg + TNFa ~ sex * male_female_iron_def, 
          
          data = id %>%
            as.data.frame(),
          FUN = function(x){paste(sprintf("%.1f", round(median(x, na.rm = T), 1)), 
                                  " (",
                                  sprintf("%.1f", round(IQR(x, na.rm = T), 1)), 
                                  ")",  sep = "")
          }, 
          keep.names = TRUE) %>%
  as_tibble() %>% t() %>% noquote()


```

Sup table 1
```{r Table 2}
table(id$acute_chronic_id_group , id$sex)

table1::table1(~ hepcidin | sex * nationals,
               data = fsd,
               overall = FALSE)

library(flextable)

summaryBy(formula = hgb + hct + ferritin + hepcidin + 
            stfr + ery_cor + bili + percent_retic + IL1a + IL1b + IL2 + 
            IL4 + IL6 +IL8 + IL10+ IL12p70 + IFNg + TNFa ~ sex,
          data = fsd %>%
            as.data.frame(),
          FUN = function(x){avg_sd_fxn(x, include.n = FALSE)}, 
          keep.names = TRUE) %>%
  as_tibble() %>% t() %>% noquote()


table(id$iron_def_avg)
summaryBy(formula = hgb + hct + ferritin + hepcidin + stfr +
            ery_cor + bili + percent_retic + IL1a + IL1b + IL2 +  
            IL4 + IL6 +IL8 + IL10+ IL12p70 + IFNg + TNFa ~ sex * nationals, 
          
          data = fsd %>%
            as.data.frame(),
          FUN = function(x){paste(sprintf("%.1f", round(median(x, na.rm = T), 1)), 
                                  " (",
                                  sprintf("%.1f", round(IQR(x, na.rm = T), 1)), 
                                  ")",  sep = "")
          }, 
          keep.names = TRUE) %>%
  as_tibble() %>% t() %>% noquote()

library(tableone)

myvars <- c("hgb", "hct", "ferritin", "hepcidin", "stfr",
            "ery_cor", "bili", "percent_retic", "IL1a", "IL1b", "IL2", 
            "IL4", "IL6", "IL8", "IL10", "IL12p70", "IFNg", "TNFa")

nonnormal <- c("hepcidin", "ery_cor", "IL1a", "IL1b", "IL2", 
               "IL4", "IL6", "IL8", "IL10", "IL12p70", "IFNg", "TNFa")


tab3 <- CreateTableOne(vars = myvars, 
                       strata = "nationals" , 
                       data = fsd %>% filter(sex == "Female"))
print(tab3, nonnormal = nonnormal, formatOptions = list(big.mark = ","))


data %>% 
  filter(!is.na(hct), sex == "Male") %>%
  summarise(pct = (sum(hct > 51.0 | hct < 37.5)/length(hct)))

data %>% 
  filter(!is.na(hct), sex == "Female") %>%
  summarise(pct = (sum(hct > 46.6 | hct < 34.0)/length(hct)))


```



Figure 1
```{r figure 1, echo = FALSE, message = FALSE, warning=FALSE}
##  Chronic  ################################################   
chronic_mod <- brglm(iron_def_avg ~   sex,
                     data = fsd %>% droplevels(),
                     family = binomial(link = "logit"))


# summary(mod)
chronic_means <- emmeans(chronic_mod, ~  sex, type = "response") %>% 
  as_tibble() %>% 
  filter(!is.na(prob)) %>% 
  mutate_if(is.numeric, function(x){100*x}) %>% 
  mutate(id = "A) Chronic ID")


##  Acute  ################################################  

acute_mod <- brglm(iron_def_once ~  sex,
                   data = fsd %>% filter(group != "Controls") %>% droplevels(),
                   family = binomial(link = "logit"))
# summary(mod)
acute_means <- emmeans(acute_mod, ~  sex, type = "response") %>% 
  as_tibble() %>% 
  filter(!is.na(prob)) %>% 
  mutate_if(is.numeric, function(x){100*x}) %>% 
  mutate(id = "B) Acute or Chronic ID")


means <- rbind(acute_means, chronic_means) %>% mutate(id = as_factor(id) %>% fct_relevel("A) Chronic ID"))

# x <- emmeans(mod, pairwise ~ nationals, type = "response")
# confint(x)
# Graph



# Create annotations

anno <- data.frame(x1 = c(1.7), x2 = c(2.3),
                   y1 = c(70), y2 = c(72), 
                   xstar = c(2), ystar = c(78),
                   lab = c("†"),
                   nationals = c("NCAA Qualifiers"),
                   id = c("B) Acute or Chronic ID"),
                   sex = c("Female"))

qualif <- data.frame(xstar = c(2), ystar = c(75),
                     lab = c("*"),
                     group = c(1),
                     # nationals = c("NCAA Qualifiers"), 
                     id = c("B) Acute or Chronic ID"),
                     sex = c("Female"))




(fig_1_xc <- ggplot(means, aes(y = prob, x = sex)) +
    geom_bar(stat ='identity', 
             # position = position_dodge(.95), 
             color = "black", fill="grey90") +
    geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL),
                  width=.04,
                  # position = position_dodge(.95)
    )+
    coord_cartesian(ylim = c(0,100)) +
    ylab("Percent of Group (%)") +
    xlab(NULL) + 
    facet_wrap(~id) + 
    theme(strip.text.x = element_text(hjust = -.01),
          axis.text.x = element_text(angle = 45, 
                                     vjust = 1,
                                     hjust = 1, 
                                     size  = 15), 
          legend.position = "right") + 
    geom_text(data = qualif, aes(x = xstar,  y = ystar, label = lab),
              color = "black", size = 9))

n <- 1
dir_fig <- "C:/Users/jagoodri/OneDrive - University of Southern California/AESL/Pac12 Research/" 
ggsave(plot = fig_1_xc, paste(dir_fig, 
                              "Manuscripts/XC Biomarkers/XC_Figure_2.jpg", sep =""),
       width = n*5.5, height = n*6)

rm(anno, qualif)
here::here()

```



# Ferritin 
```{r average ferritin, echo = FALSE, message = FALSE, warning=FALSE}
anno <- data.frame(xstar = c(2,2,3), ystar = c(30, 30, 30),
                   lab = c("*", "*","*"), sex = c("Male", "Female", "Female"))

(fer <- ggplot(id %>% filter(!is.na(acute_chronic_id_group)), 
               aes(y = ferritin, x = acute_chronic_id_group, fill = sex)) + 
    geom_boxplot(outlier.alpha = .3) +
    geom_hline(yintercept = 25, linetype = 2, color = "grey20") + 
    ylab("Ferritin (ng/mL)") + 
    xlab(NULL) + 
    scale_y_log10(breaks = c(10,25,50,100,175)) +
    theme(axis.text.x = element_blank(),
          legend.position = "none",
          strip.text.x = element_text(size = 15),
          plot.title = element_text(size=20, hjust = -.1)) +
    scale_fill_manual(values = c("grey50", "grey90")) +
    facet_grid(~sex, scales = "free_x", space = "free_x") +
    ggtitle("A)")+ 
    geom_text(data = anno, aes(x = xstar,  y = ystar, label = lab), inherit.aes = FALSE,
              color = "black", size = 9))
```


# sTfR / Ferritin ratio   
**Higher sTfR/log ferritin ratio indicate Iron Deficiency**    
* Controls higher than other groups
* Both Acute and Chronic ID XC are higher than non ID XC
```{r sTfR fer, echo = FALSE, message = FALSE, warning=FALSE}

anno <- data.frame(xstar = c(2,2,3), ystar = c(11, 12,11),
                   lab = c("*", "*","*"), sex = c("Male", "Female", "Female"))


(stfrfer <- ggplot(id, 
                   aes(y = stfr, x = acute_chronic_id_group, fill = sex)) +
    geom_boxplot(outlier.alpha = .3) +
    xlab(NULL)  +
    theme(axis.text.x = element_blank(),
          legend.position = "none",
          strip.text.x = element_text(size = 15),
          plot.title = element_text(size=20, hjust = -.1)) +
    scale_fill_manual(values = c("grey50", "grey90")) +
    facet_grid(~sex, scales = "free_x", space = "free_x") +
    ggtitle("B)")+  
    scale_y_log10()+
    ylab("sTfR"))
```

Hb concentration
```{r average hemoglobin concentration, echo = FALSE, message = FALSE, warning=FALSE}
anno <- data.frame(xstar = c(2, 2,3), ystar = c(17, 16.5, 16),
                   lab = c("*", "*", "**"), sex = c("Male", "Female", "Female"))
hb_ref <- tibble(sex = factor(c("Male", "Female"), levels = c("Male", "Female")), lower_limit = c(13.5, 12.5))



(hb <- ggplot(id,
              aes(y = hgb, x = acute_chronic_id_group, fill = sex)) + 
    geom_boxplot(outlier.alpha = .3) +
    # geom_jitter() +
    geom_hline(data = hb_ref, 
               aes(yintercept = lower_limit), 
               linetype = 2, 
               color = "grey20") +
    coord_cartesian(ylim = c(11, 19)) +
    ylab("[Hb] (g/dL)") +
    xlab(NULL) + 
    theme(axis.text.x = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(margin = margin( l = 2)),
          strip.text.x = element_text(size = 15),
          plot.title = element_text(size=20, hjust = -.1)) +
    facet_grid(~sex, scales = "free_x", space = "free_x") +
    scale_fill_manual(values = c("grey50", "grey90")) +
    scale_y_continuous(breaks = c(12,14, 16,18)) +
    ggtitle("B)")+
    geom_text(data = anno, aes(x = xstar,  y = ystar, label = lab), inherit.aes = FALSE,
              color = "black", size = 9))

```

# Hepcidin   
```{r, echo = FALSE, message = FALSE, warning=FALSE}
anno <- data.frame(xstar = c(2, 2, 3), ystar = c(50, 280,75),
                   lab = c("*", "*", "*"), sex = c("Male", "Female", "Female"))

(hep <- ggplot(id, 
               aes(y = hepcidin, x = acute_chronic_id_group, fill = sex)) + 
    geom_boxplot(outlier.alpha = .3) +
    ylab( "Hepcidin (ng/mL)") +
    xlab(NULL) + 
    scale_y_log10(limits = c(5, 300)) +
    theme(legend.position = "none",
          strip.text.x = element_blank(),
          axis.text.x = element_text(angle = 0, vjust = 0., hjust = 0.5, size = 13), 
          plot.title = element_text(size=20, hjust = -.1)) +
    facet_grid(~sex, scales = "free_x", space = "free_x") +
    scale_fill_manual(values = c("grey50", "grey90")) +
    ggtitle("C)")+
    geom_text(data = anno, aes(x = xstar,  y = ystar, label = lab), inherit.aes = FALSE,
              color = "black", size = 9))
```





# Erythroferrone
```{r, echo = FALSE, message = FALSE, warning=FALSE}

(erfe <- ggplot(id %>% filter(ery_cor > 0.1), 
                aes(y = ery_cor, x = acute_chronic_id_group, fill = sex)) + 
   geom_boxplot(outlier.alpha = .3) +
   ylab("Erythroferrone (ng/mL)") +
   xlab(NULL) + 
   scale_y_log10() +
   theme(legend.position = "none",
         strip.text.x = element_blank(),
         axis.text.x = element_text(angle = 0, vjust = 0., hjust = 0.5, size = 13), 
         plot.title = element_text(size=20, hjust = -.1)) +
   facet_grid(~sex, scales = "free_x", space = "free_x") +
   scale_fill_manual(values = c("grey50", "grey90")) +
   ggtitle("E)"))
```

# IL-6 

```{r, echo = FALSE, message = FALSE, warning=FALSE}
(IL6 <- ggplot(id, 
               aes(y = IL6, x = acute_chronic_id_group, fill = sex)) + 
   geom_boxplot(outlier.alpha = .3) +
   ylab( "IL-6 (pg/mL)") +
   xlab(NULL) + 
   scale_y_log10() +
   theme(legend.position = "none",
         strip.text.x = element_blank(),
         axis.text.x = element_text(angle = 0, vjust = 0., hjust = 0.5, size = 13), 
         plot.title = element_text(size=20, hjust = -.1)) +
   facet_grid(~sex, scales = "free_x", space = "free_x") +
   scale_fill_manual(values = c("grey50", "grey90")) +
   ggtitle("D)"))
```


# LDH

```{r, echo = FALSE, message = FALSE, warning=FALSE}
(LDH <- ggplot(id,
               aes(y = ldh, x = acute_chronic_id_group, fill = sex)) +
   geom_boxplot(outlier.alpha = .3) +
   ylab( "LDH (IU/L)") +
   xlab(NULL) +
   scale_y_log10() +
   theme(legend.position = "none",
         strip.text.x = element_blank(),
         axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 15),
         plot.title = element_text(size=20, hjust = -.1)) +
   facet_wrap(~sex, scales = "free_x")+
   scale_fill_manual(values = c("grey50", "grey90")))
```



# Figure 2

```{r figure 2, fig.height= 12, fig.width = 5, echo = FALSE, message = FALSE, warning=FALSE}


grid::grid.newpage()

# For all 6 plots: 
# grobz <- lapply(list(fer, stfrfer, hb, hep, erfe, IL6), ggplotGrob)
# 
# grobz.plot <- arrangeGrob( grobs = list(rbind(grobz[[1]], grobz[[4]], size = "last"),
#                                         rbind(grobz[[2]], grobz[[5]], size = "last"), 
#                                         rbind(grobz[[3]], grobz[[6]], size = "last")),
#                            ncol = 3)
# grid.draw(grobz.plot)


grid::grid.newpage()
grobz <- lapply(list(fer, hb, hep, IL6), ggplotGrob)

grobz.plot <- arrangeGrob( grobs = list(rbind(grobz[[1]], grobz[[3]], size = "last"),
                                        rbind(grobz[[2]], grobz[[4]], size = "last")),
                           ncol = 2)
grid.draw(grobz.plot)


n = 1.2
ggsave(plot = grobz.plot, "~/AESL/Pac12 Research/Manuscripts/XC Biomarkers/XC_Figure_2.jpg", width = n*10, height = n*6)

# grid.arrange(fer, stfrfer, hb, hep, erfe, IL6, nrow = 2)

```



Figure 3
```{r figure 3, fig.height= 12, fig.width = 5, echo = FALSE, message = FALSE, warning=FALSE}
library(pROC)
library(OptimalCutpoints)
library(fANCOVA)
library(cutpointr)


table(id$iron_def_once, (id$id_group))

## Male ############################################ ############################################ ############################################


male_roc <- pROC::roc(iron_def_once ~ hepcidin, ci = TRUE,
                      data =  id %>% filter(sex == "Male") %>% 
                        droplevels())

# ci.sp.obj.male <- ci.sp(smooth(male_roc, method = "density", bw = .25), sensitivities=seq(0, 1, .01), boot.n=100)


male_cp <- cutpointr(as.data.frame(id %>% filter(sex == "Male")),
                     hepcidin,
                     iron_def_once, na.rm = TRUE,
                     method = maximize_boot_metric, boot_runs = 100, metric = youden)


se <- male_cp$sensitivity %>% round(., 2)
sp <- male_cp$specificity%>% round(., 2)
auc <- male_cp$AUC
oc <- male_cp$optimal_cutpoint
auc.cl <- cutpointr::boot_ci(male_cp,  AUC, in_bag = TRUE, alpha = 0.05)$values

cutpointr::boot_ci(male_cp,  specificity, in_bag = TRUE, alpha = 0.05)$values
# plot(oco, which = 1)




dev.off()
par(mfrow = c(1,2), cex = 1.1)
# table(ci.data$xmax, ci.data$xmin)
plot(smooth(male_roc, method = "density", bw = .25))

plot(ci.sp.obj.male, type = "shape", col = grey(level = .5, alpha=.25), border = "grey90")
segments(x0 =se , x1 = se, y0 = 0, y1 =  sp , lty = 2)
segments(x0 = se, x1 = 1, y0 = sp, y1 = sp, lty = 2)
points(x = se, y = sp, pch = 19,cex = 1.5)
text(x = .3, y = .1, labels = paste("AUC: ", round(auc, 2), "\n[95% CI: ", round(auc.cl[1], 2), " - ",  round(auc.cl[2], 2), "]", sep = "" ))
text(x = .6, y = .53, labels = paste("Optimal Cut Point:\n", round(oc, 1), " ng/mL\n", "Sens: ", se, "\nSpec:", sp, sep = ""), cex = .9)
title("Male: ID vs. Non ID", line = 2.5)



# Female, All ID ############################################ ############################################ ############################################

id <- id %>% 
  mutate(id_group = fct_collapse(acute_chronic_id, not_id = c("Acute ID", "Chronic ID")))


fem_roc <- pROC::roc(iron_def_once ~ hepcidin, ci = TRUE,
                     data =  id %>% filter(sex == "Female") %>% 
                       droplevels())

# ci.sp.fem.all <- ci.sp(smooth(fem_roc,  method = "density", bw = .1), sensitivities=seq(0, 1, .01), boot.n=100)


# fem_cp <- cutpointr(as.data.frame(id %>% filter(sex == "Female")),
#                     hepcidin,
#                     iron_def_once,
#                      na.rm = TRUE,
#                      method = maximize_boot_metric, boot_runs = 100, metric = youden)


# fem_cp   

cutpointr::boot_ci(fem_cp,  AUC, in_bag = TRUE, alpha = 0.05)

se <- fem_cp$sensitivity %>% round(., 2)
sp <- fem_cp$specificity%>% round(., 2)
auc <- fem_cp$AUC
oc <- fem_cp$optimal_cutpoint
auc.cl <- cutpointr::boot_ci(fem_cp,  AUC, in_bag = TRUE, alpha = 0.05)$values



# table(ci.data$xmax, ci.data$xmin)
plot(smooth(fem_roc, method = "density", bw = .05))

plot(ci.sp.fem.all, type = "shape", col = c(grey(level = .5, alpha=.25)), border = "grey90")
segments(x0 =se , x1 = se, y0 = 0, y1 =  sp , lty = 2)
segments(x0 = se, x1 = 1, y0 = sp, y1 = sp, lty = 2)
points(x = se, y = sp, pch = 19,cex = 1.5)
text(x = .3, y = .1, labels = paste("AUC: ", round(auc, 2), "\n[95% CI: ", round(auc.cl[1], 2), " - ",  round(auc.cl[2], 2), "]", sep = "" ))
text(x = .55, y = .6, labels = paste("Optimal Cut Point:\n", round(oc, 1), " ng/mL\n", "Sens: ", se, "\nSpec:", sp, sep = ""), cex = .9)
title("Female: ID vs. Non ID", line = 2.5)








```













# Statistial analysis

```{r}
library(lolcat)
library(sjstats)
library(performance)
library(lattice)
library(car)


table(id$ferritin < 25, id$iron_def_once)


id$iron_def_avg
# Transform and scale numeric variables of interest
dsl <- id %>% 
  select(iron_def_once, nationals, id, sex, hgb, ferritin, hepcidin, 
         stfr, ery_cor, bili, percent_retic, IL1a, IL1b, IL2, 
         IL4, IL6,IL8, IL10,  IL12p70, IFNg, TNFa) %>% 
  mutate_at(vars(hgb:TNFa), function(x){yjPower(x, 0) %>% scale(.) }) %>%
  ungroup()



# Data L 
data.l <- dsl   %>% 
  select(iron_def_once, nationals, id, sex, hgb, ferritin, hepcidin, 
         stfr, ery_cor, bili, percent_retic, IL1a, IL1b, IL2, 
         IL4, IL6,IL8, IL10,  IL12p70, IFNg, TNFa) %>% 
  pivot_longer(., hgb:TNFa, names_to = "parameter") %>% 
  # filter(sex == "Female") %>% 
  group_by(parameter) %>% droplevels()



############ Run All Stats ############ 
output <- data.l %>% 
  do(Anova(lm(value ~ nationals * sex, data = .)) %>% as_tibble(., rownames = "factor"))



output <- output %>%
  janitor::clean_names() %>%
  select(-f_value, -df, - sum_sq) %>%
  pivot_wider(.,names_from = factor, values_from = pr_f) %>% 
  ungroup() %>%
  mutate_if(is.numeric, function(x){round(x, digits = 2)}) %>% 
  arrange(factor(parameter, levels = c( "hgb",  "ferritin",  "hepcidin",  "stfr",  "ery_cor",  "bili",  "percent_retic", 
                                        "IL1a",  "IL1b",  "IL2",  "IL4",  "IL6",  "IL8",  "IL10",  "IL12p70",  "IFNg",  "TNFa")))

# IL1a + IL1b + IL2 +  IL4 + IL6 +IL8 + IL10+ IL12p70 + IFNg + TNFa 

output <- data.l %>%
  do(emmeans(lm(value ~ time_point * group + (1|id), data = .), pairwise ~ time_point)$contrasts %>% as_tibble(.))







library(sjstats)
library(performance)
library(lattice)

## Run all stats for over time ## 

dsl_time <- data %>% 
  select(date, id, sex, #hgb, ferritin, hepcidin,  stfr, ery_cor, bili, percent_retic, 
         IL1a, IL1b, IL2, 
         IL4, IL6,IL8, IL10,  IL12p70, IFNg, TNFa) %>% 
  mutate_at(vars(IL1a:TNFa), function(x){yjPower(x, 0) %>% scale(.) }) %>%
  ungroup()



# Data L 
data_l_time <- dsl_time   %>% 
  select(date, id, sex,  #hgb, ferritin, hepcidin,  stfr, ery_cor, bili, percent_retic, 
         IL1a, IL1b, IL2, 
         IL4, IL6,IL8, IL10,  IL12p70, IFNg, TNFa) %>% 
  pivot_longer(., IL1a:TNFa, names_to = "parameter") %>% 
  # filter(sex == "Female") %>% 
  group_by(parameter, sex) %>% droplevels()





############ Run over time Stats ############ 
output_time <- data_l_time %>% 
  do(Anova(lmer(value ~ date + (1|id), data = .)) %>% as_tibble(., rownames = "factor"))



output_time <- output_time %>%
  janitor::clean_names() %>%
  select(--chisq, -df, ) %>%
  pivot_wider(.,names_from = factor, values_from = pr_chisq) %>% 
  ungroup() %>%
  mutate_if(is.numeric, function(x){round(x, digits = 4)}) %>% 
  arrange(sex, factor(parameter, levels = c( "hgb",  "ferritin",  "hepcidin",  "stfr",  "ery_cor",  "bili",  "percent_retic", 
                                             "IL1a",  "IL1b",  "IL2",  "IL4",  "IL6",  "IL8",  "IL10",  "IL12p70",  "IFNg",  "TNFa")))


## Obtain Model Performance Data  
output_time <- data_l_time %>% 
  do(model_performance(lmer(value ~ date + (1|id), data = .)) %>% as_tibble(.))


temp <- output_time %>%
  janitor::clean_names() %>%
  select(-aic, -bic, -icc, -rmse )  %>% 
  ungroup() %>%
  rename(total = r2_conditional, 
         fixed = r2_marginal) %>% 
  mutate(random = total-fixed) %>% 
  mutate_if(is.numeric, function(x){round(x, digits = 4)}) %>% 
  arrange(sex, factor(parameter, levels = c( "hgb",  "ferritin",  "hepcidin",  "stfr",  "ery_cor",  "bili",  "percent_retic", 
                                             "IL1a",  "IL1b",  "IL2",  "IL4",  "IL6",  "IL8",  "IL10",  "IL12p70",  "IFNg",  "TNFa")))

# performance::icc(mod, robust = TRUE)





# model_performance(mod)





```









# Figures for presentation


# Ferritin 
```{r average ferritin, echo = FALSE, message = FALSE, warning=FALSE}
anno <- data.frame(xstar = c(2,2,3), ystar = c(30, 30, 30),
                   lab = c("*", "*","*"), sex = c("Male", "Female", "Female"))

(fer <- ggplot(id %>% filter(!is.na(acute_chronic_id_group)), 
               aes(y = ferritin, x = acute_chronic_id_group, fill = sex)) + 
    geom_boxplot(outlier.alpha = .3) +
    geom_hline(yintercept = 25, linetype = 2, color = "grey20") + 
    ylab("Ferritin (ng/mL)") + 
    xlab(NULL) + 
    scale_y_log10(breaks = c(10,25,50,100,175)) +
    theme(#axis.text.x = element_blank(),
      legend.position = "none",
      axis.text.x = element_text(angle = 0, vjust = 0., hjust = 0.5, size = 13), 
      
      strip.text.x = element_text(size = 15),
      plot.title = element_text(size=20)) +
    scale_fill_manual(values = c("grey50", "grey90")) +
    facet_grid(~sex, scales = "free_x", space = "free_x") +
    geom_text(data = anno, aes(x = xstar,  y = ystar, label = lab), inherit.aes = FALSE,
              color = "black", size = 9))
ggsave(plot = fer, "~/AESL/Pac12 Research/Manuscripts/XC Biomarkers/ferritin.jpg", width = 5.5, height = 6)

```


Hb concentration
```{r average hemoglobin concentration, echo = FALSE, message = FALSE, warning=FALSE}
anno <- data.frame(xstar = c(2, 2,3), ystar = c(17, 16.5, 16), 
                   lab = c("*", "*", "**"), sex = c("Male", "Female", "Female"))
hb_ref <- tibble(sex = factor(c("Male", "Female"), levels = c("Male", "Female")), lower_limit = c(13.5, 12.5))



(hb <- ggplot(id,
              aes(y = hgb, x = acute_chronic_id_group, fill = sex)) + 
    geom_boxplot(outlier.alpha = .3) +
    # geom_jitter() +
    geom_hline(data = hb_ref, 
               aes(yintercept = lower_limit), 
               linetype = 2, 
               color = "grey20") +
    coord_cartesian(ylim = c(11, 19)) +
    ylab("[Hb] (g/dL)") +
    xlab(NULL) + 
    theme(         axis.text.x = element_text(angle = 0, vjust = 0., hjust = 0.5, size = 13), 
                   legend.position = "none",
                   axis.text.y = element_text(margin = margin( l = 2)),
                   strip.text.x = element_text(size = 15),
                   plot.title = element_text(size=20, hjust = -.1)) +
    facet_grid(~sex, scales = "free_x", space = "free_x") +
    scale_fill_manual(values = c("grey50", "grey90")) +
    scale_y_continuous(breaks = c(12,14, 16,18)) +
    geom_text(data = anno, aes(x = xstar,  y = ystar, label = lab), inherit.aes = FALSE,
              color = "black", size = 9))
ggsave(plot = hb, "~/AESL/Pac12 Research/Manuscripts/XC Biomarkers/hb.jpg", width = 5.5, height = 6)

```

# Hepcidin   
```{r, echo = FALSE, message = FALSE, warning=FALSE}
anno <- data.frame(xstar = c(2, 2, 3), ystar = c(50, 280,75),
                   lab = c("*", "*", "*"), sex = c("Male", "Female", "Female"))

(hep <- ggplot(id, 
               aes(y = hepcidin, x = acute_chronic_id_group, fill = sex)) + 
    geom_boxplot(outlier.alpha = .3) +
    ylab( "Hepcidin (ng/mL)") +
    xlab(NULL) + 
    scale_y_log10(limits = c(5, 300)) +
    theme(legend.position = "none",
          strip.text.x = element_text(size = 15),
          
          axis.text.x = element_text(angle = 0, vjust = 0., hjust = 0.5, size = 13), 
          plot.title = element_text(size=20, hjust = -.1)) +
    facet_grid(~sex, scales = "free_x", space = "free_x") +
    scale_fill_manual(values = c("grey50", "grey90")) +
    geom_text(data = anno, aes(x = xstar,  y = ystar, label = lab), inherit.aes = FALSE,
              color = "black", size = 9))

ggsave(plot = hep, "~/AESL/Pac12 Research/Manuscripts/XC Biomarkers/hepcidin.jpg", width = 5.5, height = 6)

```





# Erythroferrone
```{r, echo = FALSE, message = FALSE, warning=FALSE}

(erfe <- ggplot(id %>% filter(ery_cor > 0.1), 
                aes(y = ery_cor, x = acute_chronic_id_group, fill = sex)) + 
   geom_boxplot(outlier.alpha = .3) +
   ylab("Erythroferrone (ng/mL)") +
   xlab(NULL) + 
   scale_y_log10() +
   theme(legend.position = "none",
         strip.text.x = element_text(size = 15),
         
         axis.text.x = element_text(angle = 0, vjust = 0., hjust = 0.5, size = 13), 
         plot.title = element_text(size=20, hjust = -.1)) +
   facet_grid(~sex, scales = "free_x", space = "free_x") +
   scale_fill_manual(values = c("grey50", "grey90")) )

ggsave(plot = erfe, "~/AESL/Pac12 Research/Manuscripts/XC Biomarkers/erfe.jpg", width = 5.5, height = 6)

```

# IL-6 

```{r, echo = FALSE, message = FALSE, warning=FALSE}
(IL6 <- ggplot(id, 
               aes(y = IL6, x = acute_chronic_id_group, fill = sex)) + 
   geom_boxplot(outlier.alpha = .3) +
   ylab( "IL-6 (pg/mL)") +
   xlab(NULL) + 
   scale_y_log10() +
   theme(legend.position = "none",
         
         axis.text.x = element_text(angle = 0, vjust = 0., hjust = 0.5, size = 13), 
         plot.title = element_text(size=20, hjust = -.1)) +
   facet_grid(~sex, scales = "free_x", space = "free_x") +
   scale_fill_manual(values = c("grey50", "grey90")))
ggsave(plot = IL6, "~/AESL/Pac12 Research/Manuscripts/XC Biomarkers/IL6.jpg", width = 5.5, height = 6)

```



# Figure 2 for presentation

```{r figure 2, fig.height= 12, fig.width = 5, echo = FALSE, message = FALSE, warning=FALSE}


grid::grid.newpage()

# For all 6 plots: 
# grobz <- lapply(list(fer, stfrfer, hb, hep, erfe, IL6), ggplotGrob)
# 
# grobz.plot <- arrangeGrob( grobs = list(rbind(grobz[[1]], grobz[[4]], size = "last"),
#                                         rbind(grobz[[2]], grobz[[5]], size = "last"), 
#                                         rbind(grobz[[3]], grobz[[6]], size = "last")),
#                            ncol = 3)
# grid.draw(grobz.plot)


grid::grid.newpage()
grobz <- lapply(list(fer, hb, hep, IL6), ggplotGrob)

grobz.plot <- arrangeGrob( grobs = list(rbind(grobz[[1]], grobz[[3]], size = "last"),
                                        rbind(grobz[[2]], grobz[[4]], size = "last")),
                           ncol = 2)
grid.draw(grobz.plot)


n = 1.2
ggsave(plot = grobz.plot, "~/AESL/Pac12 Research/Manuscripts/XC Biomarkers/XC_Figure_2.jpg", width = n*10, height = n*6)

# grid.arrange(fer, stfrfer, hb, hep, erfe, IL6, nrow = 2)

```




